\documentclass[a4paper,11pt]{article}

% Basic packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{lmodern} % Better font rendering
\usepackage{microtype} % Better typography

% Hyperref for links (loaded last to avoid conflicts)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=false,
    linkcolor=black,
    urlcolor=black,
    pdfborder={0 0 0},
    pdftitle={Dat Tran Chinh - CV},
    pdfauthor={Dat Tran Chinh}
}

% Page margins - reduced for more space
\geometry{
    left=0.5in,
    right=0.5in,
    top=0.5in,
    bottom=0.5in
}

% Page style
\pagestyle{plain}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - reduced spacing
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Custom commands - reduced spacing
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Reduced spacing for lists
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}, itemsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in, itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\LARGE \scshape Tran Chinh Dat (Blue)} \\ \vspace{2pt}
    \small +84915-101-664 $|$ \href{mailto:chinhdatds@gmail.com}{\underline{chinhdatds@gmail.com}} $|$ 
    \href{https://linkedin.com/in/chinhdat}{\underline{linkedin.com/in/chinhdat}} \\ \vspace{2pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vietnam-Korea University of IT \& Communication (VKU)}{Da Nang, Vietnam}
      {Engineer in Data Science and Artificial Intelligence, GPA: 3.4/4.0}{Aug 2021 -- Mar 2026}
      \resumeItemListStart
        \resumeItem{\textbf{Scholarships:} Full Academic Scholarship, Pacific Links Foundation (2021--2026); Academic Incentive Scholarship, VKU (2 semesters).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Backend Developer, LikeLion}{}
      {Java Spring boot, MySQL, Python}{Jun 2025 -- Jan 2026}
      \resumeItemListStart
        \resumeItem{Migrated records with zero data loss, optimizing database throughput and ensuring absolute data integrity.}
        \resumeItem{Automated payment calculation and disbursement pipelines, eliminating manual processing overhead and enhancing transaction accuracy.}
      \resumeItemListEnd
    \resumeSubheading
      {Big Data Trainee, Samsung Innovation Campus}{}
      {Apache Spark, SQL, Selenium}{Apr 2024 -- Aug 2024}
      \resumeItemListStart
        \resumeItem{Engineered highly efficient data processing pipelines using \textbf{Apache Spark} to accelerate large-scale dataset analysis.}
        \resumeItem{Automated web scraping workflows using \textbf{Selenium}, slashing manual collection time by \textbf{60\%} while guaranteeing data quality consistency.}
        \resumeItem{Delivered actionable, data-driven insights through comprehensive exploratory data analysis for a capstone project at Samsung Innovation Campus.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://github.com/datblue21/Multi-platform-logistics-management}{Multi-Platform Logistics Management System}}{2025}
      {Java, Spring Boot, MySQL, Docker}{}
      \resumeItemListStart
        \resumeItem{Architected a highly scalable RESTful backend in \textbf{Java Spring Boot} to seamlessly support multi-platform application clients.}
        \resumeItem{Developed and optimized enterprise-critical modules, including automated invoicing, secure standard authentication, and real-time analytics.}
        \resumeItem{Integrated advanced caching mechanisms to accelerate analytics query speeds and containerized deployments with \textbf{Docker} for CI/CD readiness.}
      \resumeItemListEnd
    % \resumeSubheading
    %   {\href{https://github.com/datblue21/Redis-Database}{Redis Clone In-Memory Database Engine}}{2025}
    %   {Go}{}
    %   \resumeItemListStart
    %     \resumeItem{Built a Redis-compatible in-memory database in \textbf{Go} from scratch, implementing the RESP protocol for full compatibility with standard Redis clients.}
    %     \resumeItem{Architected a single-threaded event-loop utilizing platform-specific I/O multiplexing (epoll/kqueue) and non-blocking sockets to handle thousands of concurrent connections efficiently.}
    %     \resumeItem{Implemented a 32-level Skip List data structure, achieving \textbf{O(log n)} time complexity for insertions, deletions, and ranking operations.}
    %   \resumeItemListEnd
    \resumeSubheading
      {\href{https://github.com/datblue21/Orange-Food}{Orange Food Delivery Backend API}}{2024}
      {Java, Spring Boot, Spring Security, MySQL, AWS S3}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented a secure RESTful backend in \textbf{Java Spring Boot} for a food ordering and restaurant management platform.}
        \resumeItem{Secured API endpoints using \textbf{Spring Security} and \textbf{JWT} with Role-Based Access Control (RBAC) to handle authentication and session flows.}
        \resumeItem{Integrated \textbf{AWS S3} for scalable cloud media storage alongside \textbf{MySQL} database operations optimized via \textbf{Spring Data JPA}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.12in, label={}, itemsep=0pt]
    \item  
     \textbf{Languages}: Python, Java, Go \\
     \textbf{Frameworks}: Streamlit, Spring Boot \\
     \textbf{Libraries}: NumPy, Pandas, Matplotlib, Seaborn, Selenium \\
 \end{itemize}


%-----------CERTIFICATES-----------
\section{Certificates}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://cert.efset.org/vi/9U4jQU}{EF SET English Certificate }}{Mar 2025}
      % {Official EF SET score: 60/100}{}
      {CEFR B2 - Upper Intermediate}{}
      \resumeSubheading
      {\href{https://cert.efset.org/vi/9U4jQU}{TOEIC English Certificate }}{Apr 2026}
      % {Official EF SET score: 60/100}{}
      {CEFR B1 - Intermediate}{}

    \resumeSubheading
      {\href{https://tinyurl.com/2xxoyzgk}{Samsung Innovation Campus}}{Aug 2024}
      {Big Data}{}
    % \resumeSubheading
    %   {SQL for Data Science}{2022}
    %   {University of California, Davis}{}
  \resumeSubHeadingListEnd

  \end{document}
